Removing footnotes and appendix

### 2022-01-20 data-cleaning/footnotes_appendix.Rmd
notes

@@

```{r}
alternate_rmv %>% select(id,alternative)
```

Remove text before summary of argument (already done)

```{r}
# remove text after "summary of argument" if it exists
amicus <- amicus %>% 
  mutate(txt_full = str_to_lower(txt_full),
         txt_full = str_squish(txt_full),
         txt_short = case_when(
           grepl("summary of argument", txt_full) ~ 
             gsub(pattern = ".*summary of argument", replacement = "", x = txt_full),
           grepl("summary of the argument", txt_full) ~
             gsub(pattern = ".*summary of the argument", replacement = "", x = txt_full),
           id == 861820908073 ~ gsub(pattern = ".*introduction and summary", replacement = "", 
                                     x = txt_full),
           id == 861820896073 ~ gsub(pattern = ".*introduction", replacement = "", x = txt_full),
           id == 861822667487 ~ gsub(pattern = ".*introduction", replacement = "", x = txt_full),
           T ~ ""),
         txt_short = str_squish(txt_short))
```

@@

```{r}
a <- amicus %>%
  mutate(txt_short = str_squish(txt_short),
    appendix = str_count(txt_short, "appendix"),
    appendix_1a = str_count(txt_short, "\\*1a appendix"),
    footnotes = str_count(txt_short, "footnotes"))
```

@@

@@

>>>>

**Already done to the shortened-amicus csv file, skip this**

@@

```{r}
#alternate_rmv %>% select(id,alternative)
```

Remove text before summary of argument (already done in shortened-amicus-text csv, not raw text csv.)

```{r}
# remove text after "summary of argument" if it exists
amicus <- amicus %>% 
  mutate(txt_full = str_to_lower(txt_short),
         txt_full = str_squish(txt_full),
         txt_short = case_when(
           grepl("summary of argument", txt_full) ~ 
             gsub(pattern = ".*summary of argument", replacement = "", x = txt_full),
           grepl("summary of the argument", txt_full) ~
             gsub(pattern = ".*summary of the argument", replacement = "", x = txt_full),
           id == 861820908073 ~ gsub(pattern = ".*introduction and summary", replacement = "", 
                                     x = txt_full),
           id == 861820896073 ~ gsub(pattern = ".*introduction", replacement = "", x = txt_full),
           id == 861822667487 ~ gsub(pattern = ".*introduction", replacement = "", x = txt_full),
           T ~ ""),
         txt_short = str_squish(txt_short))
```

@@

```{r}
a <- amicus %>%
  mutate(txt_short = str_squish(txt_short),
    appendix = str_count(txt_short, "appendix"),
    appendix_1a = str_count(txt_short, "\\*1a appendix|1a appendix|1 a appendix|\\*1a"),
    footnotes = str_count(txt_short, "footnotes"))
```

@@

```{r}
a %>% filter(brief== "Gonzales v Carhart. Amici Brief for Respondents (feminist), by Constitutional Law Professors et al.docx")
```

```{r}
a %>% filter(appendix_1a==0) %>% select(brief) %>% sample_n(1)
```

@@

**We don't need to worry about the 'omitted footnote' language in the text. Remove text after 'footnotes counsel of record' or 'footnotes 1' (see github issue)**
